Figures

### 2020-02-11 manuscript/data.Rmd
show qa fig
add summary table to data doc
test fig size caption, closes #25

\arrayrulecolor{white}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, dev = c("pdf"))
```

```{r maps_dot, fig.cap = "Map of lake maximum depth in the continental United States.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map-1.pdf")
```

@@

>>>>

\arrayrulecolor{white}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, dev = c("pdf"))
knitr::opts_knit$set(eval.after = "fig.cap")
```

\pagebreak

![Summary of lake depth measurements](../tables/00_data.pdf){width=65%}

```{r maps_dot, fig.cap = paste0("Map of lake maximum depth in the continental United States (", paste0(system("fsizemb ../figures/00_map-1.pdf", intern = TRUE), " MB)")), warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map-1.pdf")
# 
```

@@

```{r 00_qa, fig.cap = "Range of depth measurements for lakes with data from multiple sources.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_qa-1.pdf")
```
